---
title: "Comparison of PLPSG and SNAP datasets"
output: html_document
date: '2022-10-05'
---

### import packages
```{r, message=FALSE}
library(ggpubr) #needed for arranging multiple plots 

```

### import data files for PLPSG dataset
```{r}
source("PLPSG_ImportData.R")
```

### import data files for SNAP datasets
```{r}
source("SNAP_ImportData.R")
```

### violin plots of learning for PLPSG and SNAP datasets
```{r, message= FALSE}
learning_katie_collected <- ggplot(PLPSG_sleep_stats_wider,
  aes(y = learning,
      x = condition)) +
  ggtitle("Our learning") +
  geom_violin() + 
    ylim(-0.15,.45) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1)  +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

learning_SNAP_all <- ggplot(SNAP_behavioral_wider,
  aes(y = learning,
      x = condition)) +
  ggtitle("SNAP learning both") +
  geom_violin() + 
  ylim(-0.15,.45) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

learning_SNAP_exp1 <- ggplot(data = subset(SNAP_behavioral_wider, experiment == "one"),
  aes(y = learning,
      x = condition)) +
  ggtitle("SNAP learning exp1") +
  geom_violin() + 
    ylim(-0.15,.45) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

learning_SNAP_exp2 <- ggplot(data = subset(SNAP_behavioral_wider, experiment == "two"),
  aes(y = learning,
      x = condition)) +
  ggtitle("SNAP learning exp2") +
  geom_violin() + 
    ylim(-0.15,.45) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

figure <- ggarrange(learning_katie_collected, learning_SNAP_all,learning_SNAP_exp1, learning_SNAP_exp2,
                    labels = c("A", "B", "C","D"),
                    ncol = 2, nrow = 2)
figure
```

### violin plots of protective effect for SNAP and PLPSG datasets (last post-test - first post-test)
```{r, message= FALSE, warning = FALSE}
protective_katie_collected <- ggplot(PLPSG_sleep_stats_wider,
  aes(y = protective,
      x = condition)) +
  ggtitle("Our protective") +
  geom_violin() + 
  ylim(-.2,.175) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1)  +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

protective_SNAP_all <- ggplot(SNAP_behavioral_wider,
  aes(y = protective,
      x = condition)) +
  ggtitle("SNAP protective both") +
  geom_violin() + 
  ylim(-.2,.175) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

protective_SNAP_exp1 <- ggplot(data = subset(SNAP_behavioral_wider, experiment == "one"),
  aes(y = protective,
      x = condition)) +
  ggtitle("SNAP protective exp1") +
  geom_violin() + 
  ylim(-.2,.175) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

protective_SNAP_exp2 <- ggplot(data = subset(SNAP_behavioral_wider, experiment == "two"),
  aes(y = protective,
      x = condition)) +
  ggtitle("SNAP protective exp2") +
  geom_violin() + 
  ylim(-.2,.175) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

figure <- ggarrange(protective_katie_collected, protective_SNAP_all, protective_SNAP_exp1, protective_SNAP_exp2,
                    labels = c("A", "B", "C","D"),
                    ncol = 2, nrow = 2)
figure
```

### violin plots of consolidation for SNAP and PLPSG datasets 
```{r, message= FALSE, warning = FALSE}
consolidation_katie_collected <- ggplot(PLPSG_sleep_stats_wider,
  aes(y = consolidation,
      x = condition)) +
  ggtitle("Our consolidation") +
  geom_violin() + 
  ylim(-55,55) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1)  +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

consolidation_SNAP_all <- ggplot(SNAP_behavioral_wider,
  aes(y = consolidation,
      x = condition)) +
  ggtitle("SNAP consolidation both") +
  geom_violin() + 
  ylim(-55,55) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

consolidation_SNAP_exp1 <- ggplot(data = subset(SNAP_behavioral_wider, experiment == "one"),
  aes(y = consolidation,
      x = condition)) +
  ggtitle("SNAP consolidation exp1") +
  geom_violin() + 
  ylim(-55,55) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

consolidation_SNAP_exp2 <- ggplot(data = subset(SNAP_behavioral_wider, experiment == "two"),
  aes(y = consolidation,
      x = condition)) +
  ggtitle("SNAP consolidation exp2") +
  geom_violin() + 
  ylim(-55,55) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

figure <- ggarrange(consolidation_katie_collected, consolidation_SNAP_all, consolidation_SNAP_exp1, consolidation_SNAP_exp2,
                    labels = c("A", "B", "C","D"),
                    ncol = 2, nrow = 2)
figure
```

### Use violin plots for consolidation2 (has learning as the denominator instead)
```{r}
plot_PLPSG_consolidation2 = ggplot(PLPSG_sleep_stats_wider,
  aes(y = consolidation2,
      x = condition)) +
  ggtitle("PLPSG consolidation") +
  geom_violin() +
  ylim(-350,410) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1)  +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)


plot_SNAP_consolidation2 = ggplot(SNAP_behavioral_wider,
  aes(y = consolidation2,
      x = condition)) +
  ggtitle("SNAP consolidation both") +
  geom_violin() + 
  ylim(-350,410) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "red",
               width = 0.2)

figure <- ggarrange(plot_PLPSG_consolidation2, plot_SNAP_consolidation2,
                    labels = c("A", "B"),
                    ncol = 2, nrow = 1)
figure
```


