---
title: "PLPSG Plots of Sleep Data"
output: html_document
date: '2022-10-05'
---

### import packages
```{r, message=FALSE}
library(ggpubr) #needed for arranging multiple plots and making plots 
library(ggplot2)
library(tidyr)

```

### import data files
```{r}
source("PLPSG_ImportData.R")

```


### visualize with histogram - amount of time spent in each stage of sleep 
```{r}
plot_N1 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(N1), x = condition, na.rm = TRUE) + 
  ylab("N1 (minutes)") + 
  theme(axis.title.x = element_text(size = 9)) + 
  ylim(0, 60) +
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized



plot_N2 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(N2), x = condition,
      na.rm = TRUE) +
  ylab("N2 (minutes)") + 
  theme(axis.title.x = element_text(size=9)) + ylim(0,60) +
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_N3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(N3), x = condition,
      na.rm = TRUE) +
  ylab("N3 (minutes)") + 
  theme(axis.title.x = element_text(size=9)) + ylim(0,60) +
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_R = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(R), x = condition,
      na.rm = TRUE) +
  ylab("R (minutes)") + 
  theme(axis.title.x = element_text(size=9)) + ylim(0,60) +
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

figure <- ggarrange(plot_N1, plot_N2, plot_N3, plot_R,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1)
figure

```


### histograms instead
```{r}
# Create a function for consistent histogram plots
create_histogram <- function(data, y_var, y_label) {
  ggplot(data = data) + 
    aes(x = as.numeric(.data[[y_var]])) + 
    xlab(y_label) +
    ylab("Count") +
    theme(axis.title.x = element_text(size = 9)) + 
    geom_histogram(position = "identity", 
                   bins = 10, 
                   alpha = 0.5,  # Transparency for overlap
                   color = "black") +
    theme(legend.position = "none")  # Disable individual legends
}

# Generate the histogram plots
plot_N1 <- create_histogram(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N1", "N1 (minutes)")
plot_N2 <- create_histogram(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N2", "N2 (minutes)")
plot_N3 <- create_histogram(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N3", "N3 (minutes)")
plot_R <- create_histogram(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "R", "R (minutes)")

# Combine the plots with a common legend
figure <- ggarrange(plot_N1, plot_N2, plot_N3, plot_R,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1,
                    common.legend = TRUE, legend = "bottom")

figure


```

```{r}
# Create a function for consistent density plots
create_density <- function(data, y_var, y_label) {
  ggplot(data = data) + 
    aes(x = as.numeric(.data[[y_var]])) + 
    xlab(y_label) +
    ylab("Density") +
    theme(axis.title.x = element_text(size = 9)) + 
    geom_density(alpha = 0.5,  # Transparency for overlap
                 adjust = 1) +
    theme(legend.position = "none")  # Disable individual legends
}

# Generate the density plots
plot_N1 <- create_density(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N1", "N1 (minutes)")
plot_N2 <- create_density(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N2", "N2 (minutes)")
plot_N3 <- create_density(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N3", "N3 (minutes)")
plot_R <- create_density(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "R", "R (minutes)")

# Combine the plots with a common legend
figure <- ggarrange(plot_N1, plot_N2, plot_N3, plot_R,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1,
                    common.legend = TRUE, legend = "bottom")

figure


```

### last sleep epoch
```{r}
ggplot(subset(PLPSG_sleep_stats_wider, condition == "sleep"), aes(x = last_sleep_epoch)) + 
  geom_bar() +
  labs( 
    title = "Last Sleep Epoch", 
    x = "Last Sleep Epoch", 
    y = "Count" 
  ) + ylim(0,15) +
  theme_minimal()

```










### visualize with dot-plot - spindles correlated with recovery (our measure of consolidation )
```{r, message = FALSE}
n2n3_f3plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2andN3_F3_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N2andN3 - F3") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

n2n3_f4plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2andN3_F4_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N2andN3 - F4") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

n2n3_c3plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2andN3_C3_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N2andN3 - C3") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

n2n3_c4plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2andN3_C4_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N2andN3 - C4") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

#just n2 now
n2_f3plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2_F3_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N2 - F3") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

n2_f4plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2_F4_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N2 - F4") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

n2_c3plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2_C3_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N2 - C3") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

n2_c4plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2_C4_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N2 - C4") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)


#just n3 now 
n3_f3plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N3_F3_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N3 - F3") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

n3_f4plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N3_F4_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N3 - F4") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

n3_c3plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N3_C3_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N3 - C3") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

n3_c4plot = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N3_C4_Count), y = recovery,
      na.rm = TRUE) + 
  xlab("N3 - C4") + 
  ylab("recovery") +
  geom_point(size = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

figure <- ggarrange(n2n3_f3plot, n2n3_f4plot, n2n3_c3plot, n2n3_c4plot,
                    n2_f3plot, n2_f4plot, n2_c3plot, n2_c4plot,
                    n3_f3plot, n3_f4plot, n3_c3plot, n3_c4plot,
                    ncol = 4, nrow = 3)
figure
#yeah.. this is not what I would predict either
```

### visualize number of spindles detected during N2 and N3 
```{r}
plot_N2andN3_F3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2andN3_F3_Count), x = condition, na.rm = TRUE) + 
  ylab("N2andN3 - F3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) 

plot_N2andN3_F4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2andN3_F4_Count), x = condition, na.rm = TRUE) + 
  ylab("N2andN3 - F4") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) 

plot_N2andN3_C3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2andN3_C3_Count), x = condition, na.rm = TRUE) + 
  ylab("N2andN3 - C3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) 

plot_N2andN3_C4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2andN3_C4_Count), x = condition, na.rm = TRUE) + 
  ylab("N2andN3 - C4") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) 

figure <- ggarrange(plot_N2andN3_F3, plot_N2andN3_F4, plot_N2andN3_C3, plot_N2andN3_C4,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1)
figure


```


### visualize number of spindles detected during N2 
```{r}
plot_N2_F3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2_F3_Count), x = condition, na.rm = TRUE) + 
  ylab("N2 - F3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) 

plot_N2_F4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2_F4_Count), x = condition, na.rm = TRUE) + 
  ylab("N2 - F4") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) 

plot_N2_C3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2_C3_Count), x = condition, na.rm = TRUE) + 
  ylab("N2 - C3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2)

plot_N2_C4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2_C4_Count), x = condition, na.rm = TRUE) + 
  ylab("N2 - C4") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) 


figure <- ggarrange(plot_N2_F3, plot_N2_F4, plot_N2_C3, plot_N2_C4,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1)
figure


```

### visualize number of spindles detected during N3 
```{r}
plot_N3_F3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N3_F3_Count), x = condition, na.rm = TRUE) + 
  ylab("N3 - F3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) 

plot_N3_F4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N3_F4_Count), x = condition, na.rm = TRUE) + 
  ylab("N3 - F4") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2)

plot_N3_C3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N3_C3_Count), x = condition, na.rm = TRUE) + 
  ylab("N3 - C3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) 

plot_N3_C4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) +
    aes(y = as.numeric(Spindles_N3_C4_Count), x = condition, na.rm = TRUE) +
    ylab("N3 - C4") +
    theme(axis.title.x = element_text(size = 9)) +
    geom_violin() +
    geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) +
    stat_summary(fun.data = "mean_cl_boot",
                 geom = "crossbar",
                 colour = "grey",
                 width = 0.2) 

figure <- ggarrange(plot_N3_F3, plot_N3_F4, plot_N3_C3, plot_N3_C4,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1)
figure


```

# altogether
```{r}
figure <- ggarrange(plot_N2andN3_F3, plot_N2_F3, plot_N3_F3,
                    plot_N2andN3_F4, plot_N2_F4, plot_N3_F4,
                    plot_N2andN3_C3, plot_N2_C3, plot_N3_C3,
                    plot_N2andN3_C4, plot_N2_C4, plot_N3_C4,
                    ncol = 3, nrow = 4)
figure
```









### also show just spindles on graph
```{r}
ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2andN3_Count), x = condition, na.rm = TRUE) + 
  ylab("Spindle Count") + 
  xlab("Condition") +
  geom_violin(fill = "lightgrey", color = "black", width = 0.7) + 
  geom_boxplot(width = 0.3, fill = "white", color = "black", outlier.shape = NA) + 
  geom_jitter(width = 0.05, height = 0, size = 2, color = "black") + 
  scale_color_identity() + 
  scale_fill_identity() + 
  theme(
    aspect.ratio = 2,
    axis.title = element_text(size = 16)  # Set font size and family
  )


```
















### how much time spent in each stage - stacked plot
```{r}
library(ggplot2)
library(dplyr)

# Filter data for 'sleep' condition and reshape it to long format
PLPSG_sleep_stats_wider_longertemp <- PLPSG_sleep_stats_wider %>%
  filter(condition == "sleep") %>%
  gather(key = "sleep_stage", value = "time", N1, N2, N3, R)

# Ensure correct order of sleep stages
PLPSG_sleep_stats_wider_longertemp$sleep_stage <- factor(PLPSG_sleep_stats_wider_longertemp$sleep_stage, 
                                                          levels = c("R", "N3", "N2", "N1"))
PLPSG_sleep_stats_wider_longertemp$time <- as.numeric(PLPSG_sleep_stats_wider_longertemp$time)

# Create the stacked bar plot with y-axis range from 0 to 90 using coord_cartesian
ggplot(PLPSG_sleep_stats_wider_longertemp, aes(y = Subject, x = time)) +
  geom_col(aes(fill = sleep_stage)) +
  labs(y = "Subject", x = "Time spent asleep (minutes)", fill = "Sleep Stage") +
  theme_minimal() +
  coord_cartesian(xlim = c(0, 90)) +
  #theme(axis.text.y = element_text(angle = 30, hjust = 1)) +
  scale_fill_manual(values = c("N1" = "lightgoldenrod2", "N2" = "darkseagreen3", "N3" = "deepskyblue4", "R" = "coral2"))
```

### how much time spent in each stage - stacked plot - do percentages now 
```{r}
# Filter data for 'sleep' condition and reshape it to long format
PLPSG_sleep_stats_wider_longertemp <- PLPSG_sleep_stats_wider %>%
  filter(condition == "sleep") %>%
  gather(key = "sleep_stage", value = "percentage", perN1, perN2, perN3, perR)

# Ensure correct order of sleep stages
PLPSG_sleep_stats_wider_longertemp$sleep_stage <- factor(
  PLPSG_sleep_stats_wider_longertemp$sleep_stage,
  levels = c("perR", "perN3", "perN2", "perN1")
)

# Create the stacked bar plot with y-axis range from 0 to 100 using coord_cartesian
ggplot(PLPSG_sleep_stats_wider_longertemp, aes(y = Subject, x = as.numeric(percentage))) +
  geom_col(aes(fill = sleep_stage)) +
  labs(y = "Subject", x = "Percentage of time spent asleep", fill = "Sleep Stage") +
  theme_minimal() +
  coord_cartesian(xlim = c(0, 100)) +
  scale_fill_manual(values = c("perN1" = "lightgoldenrod2", "perN2" = "darkseagreen3", "perN3" = "deepskyblue4", "perR" = "coral2"))

```






### again for duration - not removing anyone 
```{r}
plotn1 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(N1), y = recovery, na.rm = TRUE) + 
  xlab("N1 Duration") + 
  ylab("Recovery") + 
  theme(axis.title = element_text(size = 10, family = "Times")) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  geom_text(aes(label = Subject), hjust = -0.1, vjust = -0.5, size = 2)

plotn2 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(N2), y = recovery, na.rm = TRUE) + 
  xlab("N2 Duration") + 
  ylab("Recovery") + 
  theme(axis.title = element_text(size = 10, family = "Times")) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  geom_text(aes(label = Subject), hjust = -0.1, vjust = -0.5, size = 2)

plotsws = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(N3), y = recovery, na.rm = TRUE) + 
  xlab("SWS Duration") + 
  ylab("Recovery") + 
  theme(axis.title = element_text(size = 10, family = "Times")) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  geom_text(aes(label = Subject), hjust = -0.1, vjust = -0.5, size = 2)

plotr = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(R), y = recovery, na.rm = TRUE) + 
  xlab("REM Duration") + 
  ylab("Recovery") + 
  theme(axis.title = element_text(size = 10, family = "Times")) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  geom_text(aes(label = Subject), hjust = -0.1, vjust = -0.5, size = 2)

plotswsandrem = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(N3andR), y = recovery, na.rm = TRUE) + 
  xlab("SWS and REM Duration") + 
  ylab("Recovery") + 
  theme(axis.title = element_text(size = 10, family = "Times")) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  geom_text(aes(label = Subject), hjust = -0.1, vjust = -0.5, size = 2)



figure <- ggarrange(plotn1, plotn2, plotsws, plotr, plotswsandrem,
                    ncol = 3, nrow = 2)
figure

```





### plot of sws against rem 
```{r}
fit1 <- lm(as.numeric(R) ~ as.numeric(N3), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))

ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(N3), y = as.numeric(R), na.rm = TRUE) + 
  xlab("N3 Duration") + 
  ylab("REM Duration") + 
  theme(axis.title = element_text(size = 20, family = "Times")) + 
  geom_point(aes(color = ifelse((R == 0 | N3 == 0), "Red", "Black"))) + 
  geom_smooth(method = "lm", se = FALSE) + 
  scale_color_manual(values = c("Red" = "red", "Black" = "black"), guide = "none") +
  geom_text(aes(label = Subject), hjust = -0.1, vjust = -0.5, size = 2) + 
    geom_label(aes(x = 35, y = 30), hjust = 0, 
             label = paste("p =",signif(summary(fit1)$coef[2,4], 5)))
```





