---
title: "PLPSG_Plots_SleepHistoryXBehavioral"
author: "Katie Reis"
date: "2024-12-16"
output: html_document
---

### import packages
```{r, message=FALSE}
library(ggpubr) #needed for arranging multiple plots and making plots 
library(ggplot2)
```

### import data files
```{r}
source("PLPSG_ImportData.R")
```

### make a function to create a plot
```{r}
historyplot <- function(xval, yval, xlabel, ylabel, line1x, line1y, line2x, line2y) {  
  # Subset the data
  data_sleep <- subset(PLPSG_sleep_stats_wider, condition == "sleep")
  data_wake <- subset(PLPSG_sleep_stats_wider, condition == "wake")
  
  # Fit models for sleep and wake groups
  fitsleep <- lm(as.numeric(data_sleep[[yval]]) ~ as.numeric(data_sleep[[xval]]))
  fitwake <- lm(as.numeric(data_wake[[yval]]) ~ as.numeric(data_wake[[xval]]))
  
  # Create the plot
  ggplot(data = PLPSG_sleep_stats_wider, aes(x = .data[[xval]], y = .data[[yval]], color = condition)) +
    xlab(xlabel) +
    ylab(ylabel) +
    geom_point(size = 1) +
    geom_smooth(method = "lm", se = FALSE) +
    geom_label(aes(x = line1x, y = line1y), 
               label = paste("p =", signif(summary(fitsleep)$coef[2, 4], 5)), 
               inherit.aes = FALSE, 
               hjust = 0, size = 2) +
    geom_label(aes(x = line2x, y = line2y), 
               label = paste("p =", signif(summary(fitwake)$coef[2, 4], 5)), 
               inherit.aes = FALSE, 
               hjust = 0, size = 2) +
    scale_color_manual(values = c("sleep" = "blue", "wake" = "red"))
}
```
### NOTE: 
### night before and two night before average sleep deviation from normal sleep length - a value of -2 here means that they got an average of 2 hours less sleep the nights leading up to the experiment than they normally do, a value of +2 means that they got an average of 2 hours more sleep the nights leading up to the experiment than they normally do 
### LAST NIGHT SLEEP deviation from normal sleep length - a value of -2 here means that they got an average of 2 hours less sleep the nights leading up to the experiment than they normally do, a value of +2 means that they got an average of 2 hours more sleep the nights leading up to the experiment than they normally do 

### sleep history vs block 1 (pretest) performance
```{r}
plot1 = historyplot("NightBefore_TST", "block1", "Night Before TST", "Pretest", 9, 0.32, 9.5, 0.27)
plot2 = historyplot("AverageSleep", "block1", "Average Sleep TST", "Pretest", 8.5, 0.26, 9.8, 0.34)
plot3 = historyplot("nightbefore_sleep_deviation_from_norm", "block1", "Night Before Deviation", "Pretest", 2.7, 0.2, 2.7, 0.32)
plot4 = historyplot("average_sleep_deviation_from_norm", "block1", "Average Sleep Deviation", "Pretest", 2.4, 0.24, 2.4, 0.3)


figure = ggarrange(plot1,plot2,plot3,plot4, 
                   ncol = 2, nrow = 2,
                   common.legend = TRUE, legend = "bottom")
figure
```



### sleep history vs learning
```{r}
plot1 = historyplot("NightBefore_TST", "learning", "Night Before TST", "Learning", 8.6, 0.2, 9.3, 0.14)
plot2 = historyplot("AverageSleep", "learning", "Average Sleep TST", "Learning", 9.2, 0.23, 9.8, 0.12)
plot3 = historyplot("nightbefore_sleep_deviation_from_norm", "learning", "Night Before Deviation", "Learning", 2.9, 0.2, 2.6, 0.08)
plot4 = historyplot("average_sleep_deviation_from_norm", "learning", "Average Sleep Deviation", "Learning", 2.3, 0.16, 2.4, 0.05)


figure = ggarrange(plot1,plot2,plot3,plot4, 
                   ncol = 2, nrow = 2,
                   common.legend = TRUE, legend = "bottom")
figure
```


### sleep history vs loss
```{r}
plot1 = historyplot("NightBefore_TST", "loss", "Night Before TST", "Loss", 8.6, 0.12, 9.3, 0)
plot2 = historyplot("AverageSleep", "loss", "Average Sleep TST", "Loss", 9.2, 0.12, 9.8, 0)
plot3 = historyplot("nightbefore_sleep_deviation_from_norm", "loss", "Night Before Deviation", "Loss", 2.9, 0.1, 2.8, 0)
plot4 = historyplot("average_sleep_deviation_from_norm", "loss", "Average Sleep Deviation", "Loss", 2.3, 0.1, 2.4, 0)


figure = ggarrange(plot1,plot2,plot3,plot4, 
                   ncol = 2, nrow = 2,
                   common.legend = TRUE, legend = "bottom")
figure
```


### sleep history vs recovery (separate line for wake and sleep)
```{r}
plot1 = historyplot("AverageSleep", "recovery", "Average Sleep TST", "Recovery\n(Block5-Block4)", 9.5, 0.03, 10, -0.04)
plot2 = historyplot("NightBefore_TST", "recovery", "Night Before TST", "Recovery\n(Block5-Block4)", 8.5, 0.04, 9.4, -0.01)
plot3 = historyplot("average_sleep_deviation_from_norm", "recovery", "Average Sleep Deviation from Normal Length", "Recovery\n(Block5-Block4)", 2.3, 0.01, 2.3, -0.07)
plot4 = historyplot("nightbefore_sleep_deviation_from_norm", "recovery", "Night Before Deviation from Normal Length", "Recovery\n(Block5-Block4)", 2.9, 0.03, 2.9, -0.08)


figure = ggarrange(plot1,plot2,plot3,plot4, 
                   ncol = 2, nrow = 2,
                   labels = c("A", "B", "C", "D"),
                   common.legend = TRUE, legend = "bottom")
figure
```

### sleep history vs maintenance (separate line for wake and sleep)
```{r}
plot1 = historyplot("AverageSleep", "maintenance", "Average Sleep TST", "Maintenance\n(Block6-Block5)", 8.7, 0, 9.8, -0.05)
plot2 = historyplot("NightBefore_TST", "maintenance", "Night Before TST", "Maintenance\n(Block6-Block5)", 8.9, 0, 9.2, -0.15)
plot3 = historyplot("average_sleep_deviation_from_norm", "maintenance", "Average Sleep Deviation from Normal Length", "Maintenance\n(Block6-Block5)", 2.3, -0.03, 2.3, 0.075)
plot4 = historyplot("nightbefore_sleep_deviation_from_norm", "maintenance", "Night Before Deviation from Normal Length", "Maintenance\n(Block6-Block5)", 2.9, -0.04, 2.9, 0.08)


figure = ggarrange(plot1,plot2,plot3,plot4, 
                   ncol = 2, nrow = 2,
                   labels = c("A", "B", "C", "D"),
                   common.legend = TRUE, legend = "bottom")
figure
```

### sleep history vs long term recovery (separate line for wake and sleep)
```{r}
plot1 = historyplot("AverageSleep", "longtermrecovery", "Average Sleep TST", "Long Term Recovery\n(block6-block4)", 9.3, 0, 9.8, -0.12)
plot2 = historyplot("NightBefore_TST", "longtermrecovery", "Night Before TST", "Long Term Recovery\n(block6-block4)", 8.9, 0, 9.2, -0.15)
plot3 = historyplot("average_sleep_deviation_from_norm", "longtermrecovery", "Average Sleep Deviation from Normal Length", "Long Term Recovery\n(block6-block4)", 2.3, 0.05, 1.8, -0.05)
plot4 = historyplot("nightbefore_sleep_deviation_from_norm", "longtermrecovery", "Night Before Deviation from Normal Length", "Long Term Recovery\n(block6-block4)", 2.9, 0.05, 2.9, -0.03)


figure = ggarrange(plot1,plot2,plot3,plot4, 
                   ncol = 2, nrow = 2,
                   labels = c("A", "B", "C", "D"),
                   common.legend = TRUE, legend = "bottom")
figure
```



### sleep history vs protective (separate line for wake and sleep)
```{r}
plot1 = historyplot("AverageSleep", "protective", "Average Sleep TST", "Protective\n(block6-block3)", 9.4, -0.06, 9.5, -0.15)
plot2 = historyplot("NightBefore_TST", "protective", "Night Before TST", "Protective\n(block6-block3)", 8.9, -0.06, 9, -0.15)
plot3 = historyplot("average_sleep_deviation_from_norm", "protective", "Average Sleep Deviation from Normal Length", "Protective\n(block6-block3)", -1, -0.10, -2.5, -0.08)
plot4 = historyplot("nightbefore_sleep_deviation_from_norm", "protective", "Night Before Deviation from Normal Length", "Protective\n(block6-block3)", 2.9, 0.0, -2, -0.13)


figure = ggarrange(plot1,plot2,plot3,plot4, 
                   ncol = 2, nrow = 2,
                   labels = c("A", "B", "C", "D"),
                   common.legend = TRUE, legend = "bottom")
figure
```

### make a differnt function to create a plot without the p values
```{r}
historyplot2 <- function(xval, yval, xlabel, ylabel) {  
  # Subset the data
  data_sleep <- subset(PLPSG_sleep_stats_wider, condition == "sleep")
  data_wake <- subset(PLPSG_sleep_stats_wider, condition == "wake")
  
  
  # Create the plot
  ggplot(data = PLPSG_sleep_stats_wider, aes(x = .data[[xval]], y = .data[[yval]], color = condition)) +
    xlab(xlabel) +
    ylab(ylabel) +
    geom_point(size = 1) +
    geom_smooth(method = "lm", se = FALSE) +
    scale_color_manual(values = c("sleep" = "blue", "wake" = "red")) + 
    theme(text = element_text(family = "serif"))
}


```

#plots for recovery x sleep history metrics
```{r}
plot1 = historyplot2("AverageSleep", "recovery", "Average Sleep TST", "Recovery\n(Posttest3-Posttest2)")
plot2 = historyplot2("NightBefore_TST", "recovery", "Night Before TST", "Recovery\n(Posttest3-Posttest2)")
plot3 = historyplot2("average_sleep_deviation_from_norm", "recovery", "Cumulative Restriction", "Recovery\n(Posttest3-Posttest2)")
plot4 = historyplot2("nightbefore_sleep_deviation_from_norm", "recovery", "Immediate Restriction", "Recovery\n(Posttest3-Posttest2)")


figure = ggarrange(plot2,plot1,plot4,plot3, 
                   ncol = 2, nrow = 2,
                   labels = c("A", "B", "C", "D"),
                   common.legend = TRUE, legend = "bottom")
figure

```
### make a different function for just sleep subjects
```{r}
historyplot3 <- function(xval, yval, xlabel, ylabel, line1x, line1y) {  
    data_sleep <- subset(PLPSG_sleep_stats_wider, condition == "sleep")

    fitsleep <- lm(as.numeric(data_sleep[[yval]]) ~ as.numeric(data_sleep[[xval]]))

  
  # Create the plot
  ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep"), aes(x = as.numeric(.data[[xval]]), y = as.numeric(.data[[yval]]))) +
    xlab(xlabel) +
    ylab(ylabel) +
    geom_point(size = 1) +
    geom_smooth(method = "lm", se = FALSE) + 
    geom_label(aes(x = line1x, y = line1y), 
               label = paste("p =", signif(summary(fitsleep)$coef[2, 4], 5)), 
               inherit.aes = FALSE, 
               hjust = 0, size = 3) + 
    theme(text = element_text(family = "serif"))
} 


```

#plots for N1 x sleep history metrics
```{r}
plot1 = historyplot3("nightbefore_sleep_deviation_from_norm", "N1", "Immediate Restriction", "N1 Duration (mins)",1.8,12)
plot2 = historyplot3("average_sleep_deviation_from_norm", "N1", "Cumulative Restriction", "N1 Duration (mins)",1.8,13)
plot3 = historyplot3("nightbefore_sleep_deviation_from_norm", "perN1", "Immediate Restriction", "N1 (% of TST)",1.8,16)
plot4 = historyplot3("average_sleep_deviation_from_norm", "perN1", "Cumulative Restriction", "N1 (% of TST)",1.8,17)

figure = ggarrange(plot1, plot2, plot3, plot4,
                   ncol = 2, nrow = 2,
                   labels = c("A", "B", "C", "D"),
                   common.legend = TRUE, legend = "bottom")
figure

```

#plots for N2 x sleep history metrics
```{r}
plot1 = historyplot3("nightbefore_sleep_deviation_from_norm", "N2", "Immediate Restriction", "N2 Duration (mins)",2.2,28)
plot2 = historyplot3("average_sleep_deviation_from_norm", "N2", "Cumulative Restriction", "N2 Duration (mins)",1.8,26)
plot3 = historyplot3("nightbefore_sleep_deviation_from_norm", "perN2", "Immediate Restriction", "N2 (% of TST)",2.2,55)
plot4 = historyplot3("average_sleep_deviation_from_norm", "perN2", "Cumulative Restriction", "N2 (% of TST)",1.8,32)

figure = ggarrange(plot1, plot2, plot3, plot4,
                   ncol = 2, nrow = 2,
                   labels = c("A", "B", "C", "D"),
                   common.legend = TRUE, legend = "bottom")
figure

```

#plots for N3 x sleep history metrics
```{r}
plot1 = historyplot3("nightbefore_sleep_deviation_from_norm", "N3", "Immediate Restriction", "SWS Duration (mins)",2.2,27)
plot2 = historyplot3("average_sleep_deviation_from_norm", "N3", "Cumulative Restriction", "SWS Duration (mins)",1.8,35)
plot3 = historyplot3("nightbefore_sleep_deviation_from_norm", "perN3", "Immediate Restriction", "SWS (% of TST)",2.2,35)
plot4 = historyplot3("average_sleep_deviation_from_norm", "perN3", "Cumulative Restriction", "SWS (% of TST)",1.8,26)

figure = ggarrange(plot1, plot2, plot3, plot4,
                   ncol = 2, nrow = 2,
                   labels = c("A", "B", "C", "D"),
                   common.legend = TRUE, legend = "bottom")
figure

```

#plots for R x sleep history metrics
```{r}
plot1 = historyplot3("nightbefore_sleep_deviation_from_norm", "R", "Immediate Restriction", "REM Duration (mins)",2.2,17)
plot2 = historyplot3("average_sleep_deviation_from_norm", "R", "Cumulative Restriction", "REM Duration (mins)",1.8,15)
plot3 = historyplot3("nightbefore_sleep_deviation_from_norm", "perR", "Immediate Restriction", "REM (% of TST)",2.2,12)
plot4 = historyplot3("average_sleep_deviation_from_norm", "perR", "Cumulative Restriction", "REM (% of TST)",1.8,18)

figure = ggarrange(plot1, plot2, plot3, plot4,
                   ncol = 2, nrow = 2,
                   labels = c("A", "B", "C", "D"),
                   common.legend = TRUE, legend = "bottom")
figure

```