---
title: "PLPSG_Plots_ConsolidatorsvsNon"
author: "Katie Reis"
date: "2024-12-16"
output: html_document
---

### import packages
```{r, message=FALSE}
library(ggpubr) #needed for arranging multiple plots and making plots 
library(ggplot2)
```

### import data files
```{r}
source("PLPSG_ImportData.R")

```

### visualize with histogram - amount of time spent in each stage of sleep 
```{r}
plot_N1 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(N1), x = condition, na.rm = TRUE) + 
  ylab("N1 (minutes)") + 
  theme(axis.title.x = element_text(size = 9)) + 
  ylim(0, 60) +
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized



plot_N2 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(N2), x = condition,
      na.rm = TRUE) +
  ylab("N2 (minutes)") + 
  theme(axis.title.x = element_text(size=9)) + ylim(0,60) +
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_N3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(N3), x = condition,
      na.rm = TRUE) +
  ylab("N3 (minutes)") + 
  theme(axis.title.x = element_text(size=9)) + ylim(0,60) +
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_R = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(R), x = condition,
      na.rm = TRUE) +
  ylab("R (minutes)") + 
  theme(axis.title.x = element_text(size=9)) + ylim(0,60) +
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

figure <- ggarrange(plot_N1, plot_N2, plot_N3, plot_R,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1)
figure

```
### visualize with side by side violin plots for consolidators vs nonconsolidators 
```{r}
# Create a function for consistent plots
create_plot <- function(data, y_var, y_label) {
  ggplot(data = data) + 
    aes(y = as.numeric(.data[[y_var]]), 
        x = condition, 
        color = ifelse(recovery > 0, "Consolidators", "Non-Consolidators"), 
        fill = ifelse(recovery > 0, "Consolidators", "Non-Consolidators")) + 
    ylab(y_label) + 
    theme(axis.title.x = element_text(size = 9)) + 
    ylim(0, 60) +
    geom_violin(alpha = 0.5, color = "black") +  # Transparent violin plot
    stat_summary(fun.data = "mean_cl_boot",
                 geom = "crossbar",
                 colour = "grey",
                 alpha = 0.5,  # Add transparency to box plot
                 width = 0.2,
                 position = position_dodge(width = 0.9)) +  # Align box plots with violins
    geom_dotplot(binaxis = 'y', 
                 stackdir = 'center', 
                 dotsize = 0.5, 
                 position = position_dodge(0.9),  # Align dots with violin plots
                 alpha = 0.8) +  # Plot dots on top of box plots
    scale_color_manual(values = c("Consolidators" = "deepskyblue4", 
                                  "Non-Consolidators" = "indianred3"), 
                       name = "Group") +
    scale_fill_manual(values = c("Consolidators" = "deepskyblue4", 
                                 "Non-Consolidators" = "indianred3"), 
                      name = "Group") +
    theme(legend.position = "none")  # Disable individual legends
}

# Generate the plots
plot_N1 <- create_plot(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N1", "N1 (minutes)")
plot_N2 <- create_plot(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N2", "N2 (minutes)")
plot_N3 <- create_plot(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N3", "N3 (minutes)")
plot_R <- create_plot(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "R", "R (minutes)")

# Combine the plots with a common legend
figure <- ggarrange(plot_N1, plot_N2, plot_N3, plot_R,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1,
                    common.legend = TRUE, legend = "bottom")

figure


```


### histograms instead
```{r}
# Create a function for consistent histogram plots
create_histogram <- function(data, y_var, y_label) {
  ggplot(data = data) + 
    aes(x = as.numeric(.data[[y_var]]), 
        fill = ifelse(recovery > 0, "Consolidators", "Non-Consolidators"), 
        color = ifelse(recovery > 0, "Consolidators", "Non-Consolidators")) + 
    xlab(y_label) +
    ylab("Count") +
    theme(axis.title.x = element_text(size = 9)) + 
    geom_histogram(position = "identity", 
                   bins = 10, 
                   alpha = 0.5,  # Transparency for overlap
                   color = "black") + 
    scale_fill_manual(values = c("Consolidators" = "deepskyblue4", 
                                 "Non-Consolidators" = "indianred3"), 
                      name = "Group") +
    scale_color_manual(values = c("Consolidators" = "deepskyblue4", 
                                  "Non-Consolidators" = "indianred3"), 
                       name = "Group") +
    theme(legend.position = "none")  # Disable individual legends
}

# Generate the histogram plots
plot_N1 <- create_histogram(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N1", "N1 (minutes)")
plot_N2 <- create_histogram(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N2", "N2 (minutes)")
plot_N3 <- create_histogram(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N3", "N3 (minutes)")
plot_R <- create_histogram(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "R", "R (minutes)")

# Combine the plots with a common legend
figure <- ggarrange(plot_N1, plot_N2, plot_N3, plot_R,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1,
                    common.legend = TRUE, legend = "bottom")

figure


```

#density
```{r}
# Create a function for consistent density plots
create_density <- function(data, y_var, y_label) {
  ggplot(data = data) + 
    aes(x = as.numeric(.data[[y_var]]), 
        fill = ifelse(recovery > 0, "Consolidators", "Non-Consolidators"), 
        color = ifelse(recovery > 0, "Consolidators", "Non-Consolidators")) + 
    xlab(y_label) +
    ylab("Density") +
    theme(axis.title.x = element_text(size = 9)) + 
    geom_density(alpha = 0.5,  # Transparency for overlap
                 adjust = 1) +  # Smoothing factor, adjust as needed
    scale_fill_manual(values = c("Consolidators" = "deepskyblue4", 
                                 "Non-Consolidators" = "indianred3"), 
                      name = "Group") +
    scale_color_manual(values = c("Consolidators" = "deepskyblue4", 
                                  "Non-Consolidators" = "indianred3"), 
                       name = "Group") +
    theme(legend.position = "none")  # Disable individual legends
}

# Generate the density plots
plot_N1 <- create_density(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N1", "N1 (minutes)")
plot_N2 <- create_density(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N2", "N2 (minutes)")
plot_N3 <- create_density(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "N3", "N3 (minutes)")
plot_R <- create_density(subset(PLPSG_sleep_stats_wider, condition == "sleep"), "R", "R (minutes)")

# Combine the plots with a common legend
figure <- ggarrange(plot_N1, plot_N2, plot_N3, plot_R,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1,
                    common.legend = TRUE, legend = "bottom")

figure


```


```{r}
# Observed data
categories <- c("N1", "N2", "N3", "R")
consolidators <- c(3, 5, 6, 4)
non_consolidators <- c(1, 8, 0, 1)

# Create a data frame for ggplot
data <- data.frame(
  Epoch = rep(categories, each = 2),
  Status = rep(c("Consolidators", "Non-Consolidators"), times = 4),
  Count = c(consolidators, non_consolidators)
)

# Plot the stacked bar chart with fixed y-axis range
ggplot(data, aes(x = Epoch, y = Count, fill = Status)) + 
  geom_bar(stat = "identity", position = "stack") + 
  scale_y_continuous( 
    breaks = seq(0, max(data$Count) + 2, by = 1),  # Whole-number ticks
    limits = c(0, max(data$Count) + 2)             # Ensure proper range
  ) + 
  scale_fill_manual(values = c("Consolidators" = "deepskyblue4", 
                               "Non-Consolidators" = "indianred3")) +  # Set custom colors
  labs( 
    title = "Consolidators vs. Non-Consolidators by Last Sleep Epoch", 
    x = "Last Sleep Epoch", 
    y = "Count", 
    fill = "Status" 
  ) + 
  theme_minimal()


```



### visualize number of spindles detected during N2 and N3 
```{r}
t_test_N2andN3_F3 <- t.test(Spindles_N2andN3_F3_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
t_test_N2andN3_F4 <- t.test(Spindles_N2andN3_F4_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
t_test_N2andN3_C3 <- t.test(Spindles_N2andN3_C3_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
t_test_N2andN3_C4 <- t.test(Spindles_N2andN3_C4_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))

plot_N2andN3_F3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2andN3_F3_Count), x = condition, na.rm = TRUE) + 
  ylab("N2andN3 - F3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  geom_label(
        aes(x = 1,  # Position near the first category
            y = 800,  # Above the data
            label = paste("p =", signif(t_test_N2andN3_F3$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_N2andN3_F4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2andN3_F4_Count), x = condition, na.rm = TRUE) + 
  ylab("N2andN3 - F4") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  geom_label(
        aes(x = 1,  # Position near the first category
            y = 800,  # Above the data
            label = paste("p =", signif(t_test_N2andN3_F4$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_N2andN3_C3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2andN3_C3_Count), x = condition, na.rm = TRUE) + 
  ylab("N2andN3 - C3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  geom_label(
        aes(x = 1,  # Position near the first category
            y = 800,  # Above the data
            label = paste("p =", signif(t_test_N2andN3_C3$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_N2andN3_C4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2andN3_C4_Count), x = condition, na.rm = TRUE) + 
  ylab("N2andN3 - C4") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  geom_label(
        aes(x = 1,  # Position near the first category
            y = 800,  # Above the data
            label = paste("p =", signif(t_test_N2andN3_C4$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized


figure <- ggarrange(plot_N2andN3_F3, plot_N2andN3_F4, plot_N2andN3_C3, plot_N2andN3_C4,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1)
figure


```


### visualize number of spindles detected during N2 
```{r}
t_test_N2_F3 <- t.test(Spindles_N2_F3_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
t_test_N2_F4 <- t.test(Spindles_N2_F4_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
t_test_N2_C3 <- t.test(Spindles_N2_C3_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
t_test_N2_C4 <- t.test(Spindles_N2_C4_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))

plot_N2_F3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2_F3_Count), x = condition, na.rm = TRUE) + 
  ylab("N2 - F3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  geom_label(
        aes(x = 1,  # Position near the first category
            y = 645,  # Above the data
            label = paste("p =", signif(t_test_N2_F3$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_N2_F4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2_F4_Count), x = condition, na.rm = TRUE) + 
  ylab("N2 - F4") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  geom_label(
        aes(x = 1,  # Position near the first category
            y = 645,  # Above the data
            label = paste("p =", signif(t_test_N2_F4$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_N2_C3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2_C3_Count), x = condition, na.rm = TRUE) + 
  ylab("N2 - C3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  geom_label(
        aes(x = 1,  # Position near the first category
            y = 645,  # Above the data
            label = paste("p =", signif(t_test_N2_C3$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_N2_C4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N2_C4_Count), x = condition, na.rm = TRUE) + 
  ylab("N2 - C4") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  geom_label(
        aes(x = 1,  # Position near the first category
            y = 645,  # Above the data
            label = paste("p =", signif(t_test_N2_C4$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized


figure <- ggarrange(plot_N2_F3, plot_N2_F4, plot_N2_C3, plot_N2_C4,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1)
figure


```

### visualize number of spindles detected during N3 
```{r}
# Perform t-tests
t_test_N3_F3 <- t.test(Spindles_N3_F3_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
t_test_N3_F4 <- t.test(Spindles_N3_F4_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
t_test_N3_C3 <- t.test(Spindles_N3_C3_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
t_test_N3_C4 <- t.test(Spindles_N3_C4_Count ~ factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators")),
                       data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))

plot_N3_F3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N3_F3_Count), x = condition, na.rm = TRUE) + 
  ylab("N3 - F3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  geom_label(
        aes(x = 1,  # Position near the first category
            y = 645,  # Above the data
            label = paste("p =", signif(t_test_N3_F3$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_N3_F4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N3_F4_Count), x = condition, na.rm = TRUE) + 
  ylab("N3 - F4") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  geom_label(
        aes(x = 1,  # Position near the first category
            y = 645,  # Above the data
            label = paste("p =", signif(t_test_N3_F4$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_N3_C3 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(y = as.numeric(Spindles_N3_C3_Count), x = condition, na.rm = TRUE) + 
  ylab("N3 - C3") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_violin() + 
  geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                   fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")), 
               binaxis = 'y', stackdir = 'center', dotsize = 0.5) + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "crossbar",
               colour = "grey",
               width = 0.2) +
  geom_label(
        aes(x = 1,  # Position near the first category
            y = 645,  # Above the data
            label = paste("p =", signif(t_test_N3_C3$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
  scale_color_identity() +  # Ensures the color mapping is recognized
  scale_fill_identity()     # Ensures the fill mapping is recognized

plot_N3_C4 = ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) +
    aes(y = as.numeric(Spindles_N3_C4_Count), x = condition, na.rm = TRUE) +
    ylab("N3 - C4") +
    theme(axis.title.x = element_text(size = 9)) +
    geom_violin() +
    geom_dotplot(aes(color = ifelse(recovery > 0, "deepskyblue4", "indianred3"),
                     fill = ifelse(recovery > 0, "deepskyblue4", "indianred3")),
                 binaxis = 'y', stackdir = 'center', dotsize = 0.5) +
    stat_summary(fun.data = "mean_cl_boot",
                 geom = "crossbar",
                 colour = "grey",
                 width = 0.2) +
    geom_label(
        aes(x = 1,  # Position near the first category
            y = 645,  # Above the data
            label = paste("p =", signif(t_test_N3_C4$p.value, 5))),
        inherit.aes = FALSE,
        size = 2.5
    ) +
    scale_color_identity() +  # Ensures the color mapping is recognized
    scale_fill_identity()



figure <- ggarrange(plot_N3_F3, plot_N3_F4, plot_N3_C3, plot_N3_C4,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1)
figure


```

# altogether
```{r}
figure <- ggarrange(plot_N2andN3_F3, plot_N2_F3, plot_N3_F3,
                    plot_N2andN3_F4, plot_N2_F4, plot_N3_F4,
                    plot_N2andN3_C3, plot_N2_C3, plot_N3_C3,
                    plot_N2andN3_C4, plot_N2_C4, plot_N3_C4,
                    ncol = 3, nrow = 4)
figure
```


### Density plots of N2 and N3 spindles for consolidators and non-consolidators (recovery)
```{r}
# Plot for N2 and N3 - F3
plot_N2andN3_F3 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2andN3_F3_Count), 
      fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) + 
  xlab("N2 and N3 - F3") + 
  ylab("Density") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_density(alpha = 0.5) + 
  scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                    name = "Group") +
    geom_label(aes(x = 500,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N2andN3_F3$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
  ylim(0,0.0041)

# Plot for N2 and N3 - F4
plot_N2andN3_F4 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2andN3_F4_Count), 
      fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) + 
  xlab("N2 and N3 - F4") + 
  ylab("Density") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_density(alpha = 0.5) + 
  scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                    name = "Group") +
    geom_label(aes(x = 500,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N2andN3_F4$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
  ylim(0,0.0041)

# Plot for N2 and N3 - C3
plot_N2andN3_C3 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2andN3_C3_Count), 
      fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) + 
  xlab("N2 and N3 - C3") + 
  ylab("Density") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_density(alpha = 0.5) + 
  scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                    name = "Group") +
    geom_label(aes(x = 500,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N2andN3_C3$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
  ylim(0,0.0041)

# Plot for N2 and N3 - C4
plot_N2andN3_C4 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2andN3_C4_Count), 
      fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) + 
  xlab("N2 and N3 - C4") + 
  ylab("Density") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_density(alpha = 0.5) + 
  scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                    name = "Group") +
    geom_label(aes(x = 500,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N2andN3_C4$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
  ylim(0,0.0041)

# Arrange the plots
figure <- ggarrange(plot_N2andN3_F3, plot_N2andN3_F4, plot_N2andN3_C3, plot_N2andN3_C4,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1,
                    common.legend = TRUE, legend = "bottom")  # Adds a common legend
figure


```


### Density plots of N2 spindles for consolidators and non-consolidators (recovery)
```{r}
# Plot for N2 - F3
plot_N2_F3 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2_F3_Count), 
      fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) + 
  xlab("N2 - F3") + 
  ylab("Density") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_density(alpha = 0.5) + 
  scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                    name = "Group")  +
    geom_label(aes(x = 400,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N2_F3$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
  ylim(0,0.0041)

# Plot for N2 - F4
plot_N2_F4 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2_F4_Count), 
      fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) + 
  xlab("N2 - F4") + 
  ylab("Density") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_density(alpha = 0.5) + 
  scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                    name = "Group") +
    geom_label(aes(x = 400,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N2_F4$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
  ylim(0,0.0041)

# Plot for N2 - C3
plot_N2_C3 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2_C3_Count), 
      fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) + 
  xlab("N2 - C3") + 
  ylab("Density") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_density(alpha = 0.5) + 
  scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                    name = "Group") +
    geom_label(aes(x = 400,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N2_C3$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
  ylim(0,0.0041)

# Plot for N2 - C4
plot_N2_C4 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) + 
  aes(x = as.numeric(Spindles_N2_C4_Count), 
      fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) + 
  xlab("N2 - C4") + 
  ylab("Density") + 
  theme(axis.title.x = element_text(size = 9)) + 
  geom_density(alpha = 0.5) + 
  scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                    name = "Group") +
    geom_label(aes(x = 400,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N2_C4$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
  ylim(0,0.0041)

# Arrange the plots
figure <- ggarrange(plot_N2_F3, plot_N2_F4, plot_N2_C3, plot_N2_C4,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1,
                    common.legend = TRUE, legend = "bottom")  # Adds a common legend
figure


```



### Density plots of N3 spindles for consolidators and non-consolidators (recovery)
```{r}
# Add p-values to plots
plot_N3_F3 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) +
    aes(x = as.numeric(Spindles_N3_F3_Count),
        fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) +
    xlab("N3 - F3") +
    ylab("Density") +
    theme(axis.title.x = element_text(size = 9)) +
    geom_density(alpha = 0.5) +
    scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                      name = "Group") +
    geom_label(aes(x = 400,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N3_F3$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
    ylim(0,0.0041)


plot_N3_F4 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) +
    aes(x = as.numeric(Spindles_N3_F4_Count),
        fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) +
    xlab("N3 - F4") +
    ylab("Density") +
    theme(axis.title.x = element_text(size = 9)) +
    geom_density(alpha = 0.5) +
    scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                      name = "Group") +
    geom_label(aes(x = 400,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N3_F4$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
    ylim(0,0.0041)


plot_N3_C3 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) +
    aes(x = as.numeric(Spindles_N3_C3_Count),
        fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) +
    xlab("N3 - C3") +
    ylab("Density") +
    theme(axis.title.x = element_text(size = 9)) +
    geom_density(alpha = 0.5) +
    scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                      name = "Group") +
    geom_label(aes(x = 400,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N3_C3$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
    ylim(0,0.0041)


plot_N3_C4 <- ggplot(data = subset(PLPSG_sleep_stats_wider, condition == "sleep")) +
    aes(x = as.numeric(Spindles_N3_C4_Count),
        fill = factor(ifelse(recovery > 0, "Consolidators", "Non-Consolidators"))) +
    xlab("N3 - C4") +
    ylab("Density") +
    theme(axis.title.x = element_text(size = 9)) +
    geom_density(alpha = 0.5) +
    scale_fill_manual(values = c("Consolidators" = "deepskyblue4", "Non-Consolidators" = "indianred3"),
                      name = "Group") +
    geom_label(aes(x = 400,
                   y = 0.004,
                   label = paste("p =", signif(t_test_N3_C4$p.value, 5))),
               inherit.aes = FALSE,
               size = 2.5) +
  ylim(0,0.0041)

# Arrange the plots
figure <- ggarrange(plot_N3_F3, plot_N3_F4, plot_N3_C3, plot_N3_C4,
                    labels = c("A", "B", "C", "D"),
                    ncol = 4, nrow = 1,
                    common.legend = TRUE, legend = "bottom")

# Display the figure
figure



```

### all together 
```{r}
figure <- ggarrange(plot_N2andN3_F3, plot_N2andN3_F4, plot_N2andN3_C3, plot_N2andN3_C4,
                    plot_N2_F3, plot_N2_F4, plot_N2_C3, plot_N2_C4,
                    plot_N3_F3, plot_N3_F4, plot_N3_C3, plot_N3_C4,
                    ncol = 4, nrow = 3,
                    common.legend = TRUE, legend = "bottom")
figure
```



