---
title: "PLPSG Stats Sleep and Behavioral"
output: html_document
date: '2022-10-05'
---

### import packages
```{r, message=FALSE}
library(pander)
```

### import data files
```{r}
source("PLPSG_ImportData.R")
```

### both directions stepwise selection regression, predicting recovery from time spent in sleep stages
```{r}
#define intercept-only model
intercept_only <- lm(recovery ~ 1, data=subset(PLPSG_sleep_stats_wider, condition == "sleep"))

#define model with all predictors
all <- lm(recovery ~ as.numeric(N1) + as.numeric(N2) + as.numeric(N3) + as.numeric(R), data=subset(PLPSG_sleep_stats_wider, condition == "sleep"))

#perform backward stepwise regression
both <- step(intercept_only, direction='both', scope=formula(all), trace=0)

#view results of backward stepwise regression
pander(both$anova)

#view final model
pander(both$coefficients)

step(lm(recovery ~ as.numeric(N1) + as.numeric(N2) + as.numeric(N3) + as.numeric(R), data=subset(PLPSG_sleep_stats_wider, condition == "sleep")),direction="both")
```
### linear model predicting recovery (our measure of consolidation) from duration of N1
```{r}
n1_model = lm(recovery ~ as.numeric(N1), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
pander(summary(n1_model))
summary(n1_model)
```

### linear model predicting recovery (our measure of consolidation) from duration of N2
```{r}
n2_model = lm(recovery ~ as.numeric(N2), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
pander(summary(n2_model))
summary(n2_model)
```



### linear model predicting recovery (our measure of consolidation) from duration of N3
```{r}
n3_model = lm(recovery ~ as.numeric(N3), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
pander(summary(n3_model))
summary(n3_model)
```
### what about if we remove the subjects that didn't demonstrate any N3 
```{r}
n3_model = lm(recovery ~ as.numeric(N3), data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0))
pander(summary(n3_model))
summary(n3_model)
```
### what about if we remove the subjects that didn't demonstrate any R, does N3 now predict recovery
```{r}
n3_model = lm(recovery ~ as.numeric(N3), data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0))
pander(summary(n3_model))
summary(n3_model)
```


### linear model predicting recovery (our measure of consolidation) from duration of R
```{r}
r_model = lm(recovery ~ as.numeric(R), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
pander(summary(r_model))
summary(r_model)
```

### what about if we remove the subjects that didn't demonstrate any R 
```{r}
r_model = lm(recovery ~ as.numeric(R), data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0))
pander(summary(r_model))
summary(r_model)
```

### linear model predicting recovery (our measure of consolidation) from duration of N3 and R
```{r}
n3r_model = lm(recovery ~ as.numeric(N3andR), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
pander(summary(n3r_model))
summary(n3r_model)
```




### what about if we remove the subjects that didn't demonstrate any R or n3 - do for n3, r, and n3 plus r
```{r}
n3_model = lm(recovery ~ as.numeric(N3), data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0 & N3 > 0))
pander(summary(n3_model))
summary(n3_model)

r_model = lm(recovery ~ as.numeric(R), data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0 & N3 > 0))
pander(summary(r_model))
summary(r_model)

n3r_model = lm(recovery ~ as.numeric(N3andR), data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0 & N3 > 0))
pander(summary(n3r_model))
summary(n3r_model)
```
### NOW LOOK AT PERCENTAGE TIME SPENT IN EACH STAGE 

### linear model predicting recovery (our measure of consolidation) from percentage time spent in N1
```{r}
n1per_model = lm(recovery ~ as.numeric(perN1), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(n1per_model)
```

### linear model predicting recovery (our measure of consolidation) from percentage time spent in N2
```{r}
n2per_model = lm(recovery ~ as.numeric(perN2), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(n2per_model)
```


### linear model predicting recovery (our measure of consolidation) from percentage time spent in N3
```{r}
n3per_model = lm(recovery ~ as.numeric(perN3), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(n3per_model)
```

### linear model predicting recovery from percentage of time spent in R
```{r}
rper_model = lm(recovery ~ as.numeric(perR), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(rper_model)
```


### linear model predicting recovery from percentage of time spent in N3 and R
```{r}
n3rper_model = lm(recovery ~ as.numeric(perN3andR), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(n3rper_model)
```

### what about if we remove the subjects that didn't demonstrate any R or N3
```{r}
n3per_model = lm(recovery ~ as.numeric(perN3), data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(n3per_model)

rper_model = lm(recovery ~ as.numeric(perR), data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(rper_model)

n3andrper_model = lm(recovery ~ as.numeric(perN3andR), data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(n3andrper_model)
```
### NOW LOOK AT LATENCY 

### linear model predicting recovery from latency of N1
```{r}
latn1_model = lm(recovery ~ as.numeric(latN1), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(latn1_model)
```

### linear model predicting recovery from latency of N2
```{r}
latn2_model = lm(recovery ~ as.numeric(latN2), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(latn2_model)
```

### linear model predicting recovery from latency of N3
```{r}
latn3_model = lm(recovery ~ as.numeric(latN3), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(latn3_model)
```
### linear model predicting recovery from latency of R
```{r}
latr_model = lm(recovery ~ as.numeric(latR), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(latr_model)
```


### linear model predicting recovery from WASO
```{r}
waso_model = lm(recovery ~ as.numeric(WASO), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(waso_model)
```

### linear model predicting recovery from TST
```{r}
tst_model = lm(recovery ~ as.numeric(TST), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(tst_model)
```

### linear model predicting recovery from SE
```{r}
se_model = lm(recovery ~ as.numeric(SE), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(se_model)
```
### linear model predicting recovery from number of fragmentations 
```{r}
frag_model = lm(recovery ~ as.numeric(number_fragmentations), data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(frag_model)

```

### linear model predicting recovery from spindle count (both N2 and N3)
```{r}
spindles_consolidation_model = lm(recovery ~ as.numeric(Spindles_N2andN3_Count), 
                                  data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(spindles_consolidation_model)
```
### linear model predicting recovery from spindle count (N2)
```{r}
spindles_n2_consolidation_model = lm(recovery ~ as.numeric(Spindles_N2_Count), 
                                  data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(spindles_n2_consolidation_model)
```

### linear model predicting recovery from spindle count (N3)
```{r}
spindles_n3_consolidation_model = lm(recovery ~ as.numeric(Spindles_N3_Count), 
                                  data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(spindles_n3_consolidation_model)
```
### spindles (minus the subjects with no rem and no sws)
```{r}
#spindles
spindles_minus0sws0rem_consolidation_model = lm(recovery ~ as.numeric(Spindles_N2andN3_Count), 
                                  data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0 & N3 > 0))
pander(summary(spindles_minus0sws0rem_consolidation_model))
summary(spindles_minus0sws0rem_consolidation_model)
```

#for the folks who got 0 R or 0 N3, does anything predict their recovery?
```{r}
n1_0sws0rem_consolidation_model = lm(recovery ~ as.numeric(N1), 
                                  data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & (R == 0 | N3 == 0)))
summary(n1_0sws0rem_consolidation_model)

n2_0sws0rem_consolidation_model = lm(recovery ~ as.numeric(N2), 
                                  data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & (R == 0 | N3 == 0)))
summary(n2_0sws0rem_consolidation_model)

n3_0sws0rem_consolidation_model = lm(recovery ~ as.numeric(N3), 
                                  data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & (R == 0 | N3 == 0)))
summary(n3_0sws0rem_consolidation_model)

r_0sws0rem_consolidation_model = lm(recovery ~ as.numeric(R), 
                                  data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & (R == 0 | N3 == 0)))
summary(r_0sws0rem_consolidation_model)


```


```{r}
count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0 & N3 > 0 & recovery >= 0))
count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0 & N3 > 0 & recovery < 0))

count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R == 0 & N3 > 0 & recovery >= 0))
count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R == 0 & N3 > 0 & recovery < 0))

count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0 & N3 == 0 & recovery >= 0))
count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0 & N3 == 0 & recovery < 0))

count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R == 0 & N3 == 0 & recovery >= 0))
count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R == 0 & N3 == 0 & recovery < 0))




count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0 & N3 > 0))
count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R == 0 & N3 > 0))

count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R > 0 & N3 == 0))
count(subset(PLPSG_sleep_stats_wider, condition == "sleep" & R == 0 & N3 == 0))

```
#calculate number of transitions between each stage for consolidators and non consolidators 
```{r}



```

#calculate number of transitions between each stage for consolidators and non consolidators 
```{r}
# Convert the transition columns to numeric if they are not already
PLPSG_sleep_stats_wider[transition_columns] <- lapply(
  PLPSG_sleep_stats_wider[transition_columns],
  function(x) as.numeric(as.character(x))
)

# Group by consolidator_status and calculate averages for the specified columns
average_transitions <- PLPSG_sleep_stats_wider %>%
  group_by(consolidator_status) %>%
  summarise(across(all_of(transition_columns), mean, na.rm = TRUE)) %>%
  pivot_longer(
    cols = -consolidator_status,  # All columns except consolidator_status
    names_to = "Transition_Type",  # Column to store transition types
    values_to = "Average"          # Column to store calculated averages
  ) %>%
  pivot_wider(
    names_from = consolidator_status,  # Convert consolidator_status to columns
    values_from = Average              # Values are taken from Average column
  )

# View the result
print(average_transitions)

#look at overall averages - collapse across nonconsolidators and consolidators
# Overall averages (ignoring consolidator_status)
overall_averages <- PLPSG_sleep_stats_wider %>%
  summarise(across(all_of(transition_columns), mean, na.rm = TRUE)) %>%
  pivot_longer(
    cols = everything(),             # All transition columns
    names_to = "Transition_Type",    # Column to store transition types
    values_to = "Average"            # Column to store calculated averages
  )


# View the overall averages table
print("Overall Averages:")
print(overall_averages)

#are any of these differences statistically significant? - the answer is no 

library(broom)

# Define the columns of interest
transition_columns <- c(
  "N1_to_N2_transitions", "N1_to_N3_transitions", "N1_to_R_transitions", "N1_to_W_transitions",
  "N2_to_N1_transitions", "N2_to_N3_transitions", "N2_to_R_transitions", "N2_to_W_transitions",
  "N3_to_N1_transitions", "N3_to_N2_transitions", "N3_to_R_transitions", "N3_to_W_transitions",
  "R_to_N1_transitions", "R_to_N2_transitions", "R_to_N3_transitions", "R_to_W_transitions",
  "W_to_N1_transitions", "W_to_N2_transitions", "W_to_N3_transitions", "W_to_R_transitions"
)

# Perform t-tests for each transition column
t_test_results <- transition_columns %>%
  lapply(function(col) {
    t_test <- t.test(
      PLPSG_sleep_stats_wider[[col]] ~ PLPSG_sleep_stats_wider$consolidator_status,
      na.rm = TRUE
    )
    tidy(t_test) %>% mutate(transition = col)  # Tidy the results and add column name
  }) %>%
  bind_rows()  # Combine all results into one data frame

# View the results
print(t_test_results)

```



#what if we add loss as a predictor
```{r}
n1_model = lm(recovery ~ as.numeric(N1) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(n1_model)

n2_model = lm(recovery ~ as.numeric(N2) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(n2_model)

n3_model = lm(recovery ~ as.numeric(N3) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(n3_model)

r_model = lm(recovery ~ as.numeric(R) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(r_model)

n3r_model = lm(recovery ~ as.numeric(N3andR) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(n3r_model)

fit_lastepoch = aov(recovery ~ last_sleep_epoch + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(fit_lastepoch)

tst_model = lm(recovery ~ as.numeric(TST) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep"))
summary(tst_model)

```

#however might only want to look at subjects who spent time in all stages 
```{r}
n1_model = lm(recovery ~ as.numeric(N1) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(n1_model)

n2_model = lm(recovery ~ as.numeric(N2) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(n2_model)

n3_model = lm(recovery ~ as.numeric(N3) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(n3_model)

r_model = lm(recovery ~ as.numeric(R) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(r_model)

n3r_model = lm(recovery ~ as.numeric(N3andR) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(n3r_model)

fit_lastepoch = aov(recovery ~ last_sleep_epoch + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(fit_lastepoch)


tst_model = lm(recovery ~ as.numeric(TST) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(tst_model)

spind_model = lm(recovery ~ as.numeric(Spindles_N2andN3_Count) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(spind_model)

spindn2_model = lm(recovery ~ as.numeric(Spindles_N2_Count) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(spindn2_model)

spindn3_model = lm(recovery ~ as.numeric(Spindles_N3_Count) + loss, data = subset(PLPSG_sleep_stats_wider, condition == "sleep" & N3 > 0 & R > 0))
summary(spindn3_model)
```

```{r}
PLPSG_sleep_stats_wider
med = median(PLPSG_sleep_stats_wider$'2dprime')
PLPSG_sleep_stats_wider = PLPSG_sleep_stats_wider %>% mutate(twoback_MS = ifelse(PLPSG_sleep_stats_wider$'2dprime' > med, 1, 0))
PLPSG_sleep_stats_wider$twoback_MS = as.factor(PLPSG_sleep_stats_wider$twoback_MS)
PLPSG_sleep_stats_wider$condition = as.factor(PLPSG_sleep_stats_wider$condition)

model = lm(recovery ~ learning * twoback_MS * condition, data = subset(PLPSG_sleep_stats_wider))
summary(model)

t.test(PLPSG_sleep_stats_wider$recovery[PLPSG_sleep_stats_wider$condition == "sleep"], PLPSG_sleep_stats_wider$recovery[PLPSG_sleep_stats_wider$condition == "wake"])
```


```{r}
t.test(PLPSG_sleep_stats_wider$SS_BeforeBlock5[PLPSG_sleep_stats_wider$condition == "sleep"], PLPSG_sleep_stats_wider$SS_BeforeBlock5[PLPSG_sleep_stats_wider$condition == "wake"])


```

